Capstone Movielens Report

### 2025-12-09 reports/capstone-movielens.site/02-0.methods.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

::: {.noteblock data-latex=""}
The `K` value for the *K-Fold Cross-Validation* we use in *This Project* is determined by the length of the list composing the [`edx_CV` Object]. In our case, the length of the `edx_CV` is 5, meaning we use *5-Fold Cross-Validation*.
:::

>>>>

::: {.noteblock data-latex=""}
The $K$ value for the *K-Fold Cross-Validation* we use in *This Project* is determined by the length of the list composing the [`edx_CV` Object]. In our case, the length of the `edx_CV` is 5, meaning we use *5-Fold Cross-Validation*.
:::

### 2025-12-09 reports/capstone-movielens.site/02.4.UE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

::: {.noteblock data-latex=""}
The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).
:::

>>>>

::: {.noteblock data-latex=""}
The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).
:::

### 2025-12-09 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

Below, we provide the most significant line of the code for training our model using the `5-Fold Cross Validation` method:

Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1177) for training our model using the `K-Fold Cross Validation` method, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
```{r, eval=FALSE}
  cv.UMGY_effect <- train_UMGY_effect.cv()
```
```{r}
str(cv.UMGY_effect)
summary(cv.UMGY_effect)
```

@@

  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the `K-Fold Cross Validation` samples (in *this Project* we use `K = 5`);

>>>>

Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1177) for training our model using the *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
```{r, eval=FALSE}
  cv.UMGY_effect <- train_UMGY_effect.cv()
```
```{r}
str(cv.UMGY_effect)
summary(cv.UMGY_effect)
```

@@

  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *K-Fold Cross Validation* samples (in *this Project* we use $K = 5$);

### 2025-12-09 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) for training our model using the `K-Fold Cross Validation` method, where the `K` is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use `K = 5`):
```{r, eval=FALSE}
  cv.UMGYDE.default_params <- train_UMGY_SmoothedDay_effect.cv()
```
```{r}
str(cv.UMGYDE.default_params)
```

>>>>

Below, we provide the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) for training our model using the *K-Fold Cross Validation* method, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
```{r, eval=FALSE}
  cv.UMGYDE.default_params <- train_UMGY_SmoothedDay_effect.cv()
```
```{r}
str(cv.UMGYDE.default_params)
```

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Refactoring (in progress): K-Fold Cross-Validation references.

::: { #func.mse_cv.args.r_list .sidebar }
  - **r_list:** A list of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case Study: Recommender Systems / Loss Function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the *Course Textbook (New Edition)*[@IDS2_24-1_LF], computed in the corresponding iteration of *K-fold cross-validation* (the $K$ is $5$ for *this Project*).

@@

The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).

@@

The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the `K` value is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

:::
::: { #func.train_user_movie_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

::: { #func.train_user_movie_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

::: {.noteblock data-latex=""}
The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::
:::

@@

Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The `K` value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::
:::

@@

The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The `K` value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::
:::

@@

The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).

@@

:::
::: { #func.train_user_movie_genre_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

::: { #func.train_user_movie_genre_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).

@@

:::
::: { #func.calc_date_general_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

::: { #func.calc_date_general_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

:::
::: { #func.train_UMGY_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

::: { #func.train_UMGY_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).

@@

::: { #func.calc_day_general_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

:::
::: { #func.train_UMGY_SmoothedDay_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

::: { #func.train_UMGY_SmoothedDay_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter.

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the `K` is the length of the [`edx_CV` Object] (in *this Project* we use `K = 5`).
:::

@@

@@

Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of `K` is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use `K = 5`).

@@

The `K` value for the *K-Fold Cross-Validation* is determined by the length of the list composing the `edx_CV` object. In *this Project*, we choose `K = 5`.

>>>>

::: { #func.mse_cv.args.r_list .sidebar }
  - **r_list:** A list of numeric vectors, each representing a set of residuals as described in [Section 24.1 *Case Study: Recommender Systems / Loss Function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the *Course Textbook (New Edition)*[@IDS2_24-1_LF], computed in the corresponding iteration of *K-Fold Cross-Validation* (the $K$ is $5$ for *this Project*).

@@

The Mean Squared Error (MSE) values obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the $K$ value is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).

@@

The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] described below in the [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).

@@

The Root Mean Squared Errors (RMSE) value obtained from applying the *K-Fold Cross-Validation* method to the *Overall Average Rating (OMR) Model*, where the $K$ value is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

:::
::: { #func.train_user_movie_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

::: { #func.train_user_movie_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

::: {.noteblock data-latex=""}
The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::
:::

@@

Data frame representing the *UM Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::
:::

@@

The *MSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

The $K$ value for the *K-Fold Cross-Validation* method is determined by the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::
:::

@@

The *RMSE* value calculated for the *UM Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

Internally it uses the [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) and [calc_user_movie_effect_RMSE.cv](#func.calc_user_movie_effect_RMSE.cv) functions described above to validate the *UME Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).

@@

:::
::: { #func.train_user_movie_genre_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

::: { #func.train_user_movie_genre_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

Data frame representing the *UMG Effect Model* trained (and also *regularized* if the [lambda](#func.train_user_movie_genre_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

The *MSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

The *RMSE* value calculated for the *UMG Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

Internally it uses the [train_user_movie_genre_effect.cv](#func.train_user_movie_genre_effect.cv) and [calc_user_movie_genre_effect_RMSE.cv](#func.calc_user_movie_genre_effect_RMSE.cv) functions described above to validate the *UMGE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).

@@

:::
::: { #func.calc_date_general_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

::: { #func.calc_date_general_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

:::
::: { #func.train_UMGY_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

::: { #func.train_UMGY_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

The *MSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

The *RMSE* value calculated for the *UMGY Effect Model* with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).

@@

::: { #func.calc_day_general_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

:::
::: { #func.train_UMGY_SmoothedDay_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

::: { #func.train_UMGY_SmoothedDay_effect.cv.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

@@

Data frame representing the *UMGY Effect Model* trained (and also *regularized* if the [lambda](#func.train_UMGY_SmoothedDay_effect.cv.args.lambda) argument value is other than the default) with use of *K-Fold Cross-Validation*, where the $K$ is the length of the [`edx_CV` Object] (in *this Project* we use $K = 5$).
:::

@@

#### [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) Function {#func.regularize.train_UMGYD_effect}
\

Trains (and optionally *regularizes* if the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) the *User+Movie+Genre+Year Effect (UMGYDE) Model* using the training sample of the `Movielens` dataset passed in the [train_set](#func.regularize.train_UMGYD_effect.args.train_set) argument.

::: { #func.regularize.train_UMGYD_effect.usage .sidebar }
##### Usage
\

::: { #func.regularize.train_UMGYD_effect.args .sidebar }
##### Arguments
\

::: { #func.regularize.train_UMGYD_effect.args.train_set .sidebar }
  - **train_set:** Training sample of the `Movielens` dataset;

:::
::: { #func.regularize.train_UMGYD_effect.args.lambda .sidebar }
  - **lambda:** (0 by default) Regularization parameter $\lambda$.

::: { #func.regularize.train_UMGYD_effect.details .sidebar }
##### Details
\

::: {.noteblock data-latex=""}
The *Regularization technique* described in [Section 24.2 *Penalized least squares*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) of the _Course Textbook (New Edition)_[@IDS2_24-2] is applied to the model being trained only when the *regularization parameter* $\lambda$ passed in the [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument, has a value other than the default (to be more exact, greater than zero).
:::
:::

::: { #func.regularize.train_UMGYD_effect.value .sidebar }
##### Value
\

Data frame representing the trained (and also *regularized* if [lambda](#func.regularize.train_UMGYD_effect.args.lambda) argument value is non-default) *UMGY Effect Model*.
:::

::: { #func.regularize.train_UMGYD_effect.code .sidebar }
##### Source Code
\

The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [regularize.train_UMGYD_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) function is also available in the [Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L3) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L99) script on _GitHub_.
:::
:::

@@

Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).

@@

The $K$ value for the *K-Fold Cross-Validation* is determined by the length of the list composing the `edx_CV` object. In *this Project*, we choose $K = 5$.
